Changelog

### 2021-05-25 changelog.tex
Updates from Overleaf

a. The methods in my dissertation can not find all kinds of side-channel leakages. No tool can find all forms of leakages. Even for address-based side-channel leakages, Abacus and Quincunx can not find all the leakages due to the code coverage problem. Some verification tools can prove the absence of side-channel leakages for some small code snippets. However, to the best of my knowledge, one tools as yet can prove the absence of side-channel leakages in production software.

@@

c. The research in the dissertation can only handle address-based side-channel attacks. Many side-channel attacks infer secret data based on other side-channel signals (e.g, timing, EM signals). However, the root cause of these attacks is still the same. That is, the program accesses different addresses when it processes different input secrets. Under the circumstance, our methods can still detect these attacks.

@@

a. Abacus quantifies the amount of leaked information for a given address access behavior.

b. Quincunx defines the amount of leaked information by the empirical entropy of the observations. For a determinism program, channel capacity is the tight upper bound of the the empirical entropy of the observations. That's why I used the term ``lower bound'' during my PhD defense. I have removed the term ``lower bound'' right know.

>>>>

a. The methods in my dissertation can not find all kinds of side-channel leakages. No tool can find all forms of leakages. Even for address-based side-channel leakages, Abacus and Quincunx can not find all the leakages due to the code coverage problem. Some verification tools can prove the absence of side-channel leakages for some small code snippets. However, to the best of my knowledge, no tools as yet can prove the absence of side-channel leakages in production software.

@@

c. The research in the dissertation can only handle address-based side-channel attacks. Many side-channel attacks infer secret data based on other side-channel signals (e.g, timing, EM signals). However, the root cause of these attacks is still the same. That is, the program accesses different addresses when it processes different input secrets. Under the circumstance, our methods can still detect these leakage sites.

@@

a. Abacus quantifies the amount of leaked information for a given address access behavior. It is a measure of the amount of leaked information that an attacker can get, given that another event has already occurred.

b. Quincunx defines the amount of leaked information by the empirical entropy of the observations. For a determinism program, channel capacity is the tight upper bound of the the empirical entropy of the observation. That's why I used the term ``lower bound'' during my PhD defense. I have removed the term ``lower bound'' to avoid any confusion in my dissertation.
